R Notebook

### 2021-02-20 outputs/paper/paper.Rmd
add lorena's text and update graphs

<<<<tells a reader everything they need to know, including putting it into a broader context.>>>>

The experiment was comissioned by ___.

<<<<<<you’re interested in, what you did, what you found, why it’s important, etc.>>>>>>>>

<<<Outline paper structure>>>

@@

```{r treatmentcontrolgroups, echo = FALSE, message = FALSE, warning = FALSE}
treatment_control_groups %>%
  knitr::kable(caption = "Cluster sample randomly selecting Local Health Authorities from strata based on population size",
               booktabs = TRUE) %>%
  kableExtra::kable_styling()
```

@@

This survey cost $5,606. A detailed breakdown of costs can be found on [Appendix A](#appendixA).

@@

survey_2 <- read_csv(here("outputs/data/survey_2.csv")) %>%
    mutate(group = fct_relevel(group, "treatment", "control"),
           service_type = fct_relevel(service_type, "dinein", "takeout", "both"),
           disability = fct_relevel(disability, "yes", "no", "nonanswer"),
           woman = fct_relevel(woman, "yes", "no", "nonanswer"),
           indigenous = fct_relevel(indigenous, "yes", "no", "nonanswer"),
           visible = fct_relevel(visible, "yes", "no", "nonanswer"))
```

@@

It was necessary to collect data before the intervention to establish that the treatment and control groups were in fact comparable.

Survey 1 data as baseline  Table \@ref(tab:survey1summary) Figure \@ref(fig:baselinerevenue) Figure \@ref(fig:baselineemployees)

@@

```{r survey1summary, echo = FALSE, message = FALSE, warning = FALSE}
survey_1 %>% 
  summary_factorlist("group", c("service_type", "disability", "woman", "indigenous", "visible", "revenue", "ft", "pt"),
                     p = FALSE, 
                     add_dependent_label = TRUE, 
                     dependent_label_prefix = "",
                     add_col_totals = TRUE,
                     include_row_missing_col = FALSE,
                     col_totals_rowname = "",
                     col_totals_prefix = "N = ",
                     total_col = FALSE) %>%
  mutate(group = c("", "Service type", "", "", "Owner has disability", "", "", "Owner identifies as woman", "", "", "Owner is indigenous", "", "", "Owner is a visible minority (non-Indigenous)", "", "", "Revenue", "Number of full-time employees", "Number of part-time employees")) %>%
  knitr::kable(caption = "Summary statistics for treatment and control baselines",
               booktabs = TRUE,
               col.names = c("", "", "Treatment", "Control")) %>%
  kableExtra::kable_styling(latex_options = "striped", stripe_index =c(1,5:7,11:13,17:19))
```

```{r baselinerevenue, fig.cap="Revenue distribution for treatment and control baselines, from Survey 1", fig.width=10, fig.height=4, echo = FALSE, message = FALSE, warning = FALSE}
ggplot(survey_1, aes(x = revenue / 1000, fill = group)) +                       
  geom_histogram(position = "dodge", binwidth = 5) +
  theme_minimal() +
  scale_x_continuous(limits = c(0, 250), breaks = c(0, 50, 100, 150, 200, 250, 300)) +
  labs(fill = NULL,
       x = "Revenue in May 2021 (in thousands of Canadian dollars)",
       y = "Number of restaurants")
```

@@

grid.arrange(p1, p2, ncol = 2)
```

@@

Survey 2 data to contrast treatment and control. Table \@ref(tab:survey2summary)

```{r survey2summary, echo = FALSE, message = FALSE, warning = FALSE}
survey_2 %>% 
  summary_factorlist("group", c("service_type", "disability", "woman", "indigenous", "visible", "shutdown", "revenue", "ft", "pt"),
                     p = FALSE, 
                     add_dependent_label = TRUE, 
                     dependent_label_prefix = "",
                     add_col_totals = TRUE,
                     include_row_missing_col = FALSE,
                     col_totals_rowname = "",
                     col_totals_prefix = "N = ",
                     total_col = FALSE) %>%
  mutate(group = c("", "Service type", "", "", "Owner has disability", "", "", "Owner identifies as woman", "", "", "Owner is indigenous", "", "", "Owner is a visible minority (non-Indigenous)", "", "", "Closure", "", "", "Revenue", "Number of full-time employees", "Number of part-time employees")) %>%
  knitr::kable(caption = "Summary statistics for treatment and control groups post-treatment",
               booktabs = TRUE,
               col.names = c("", "", "Treatment", "Control")) %>%
   kableExtra::kable_styling(latex_options = "striped", stripe_index =c(1,5:7,11:13,17:19))
```

@@

<<< overview of the results>>>

<<<how they fit in existing literature -- need some references here>>>>

@@

```{r postrevenue, fig.cap="Revenue distribution for treatment and control groups, from Survey 2", fig.width=10, fig.height=4, echo = FALSE, message = FALSE, warning = FALSE}
ggplot(survey_2, aes(x = revenue / 1000, fill = group)) +                       
  geom_histogram(position = "dodge", binwidth = 5) +
  theme_minimal() +
  scale_x_continuous(breaks = c(0, 50, 100, 150, 200, 250, 300)) +
  labs(fill = NULL,
       x = "Revenue in July 2021 (in thousands of Canadian dollars)",
       y = "Number of restaurants")
```

@@

grid.arrange(p1, p2, ncol = 2)
```

@@

```{r servicetypeimpact, fig.cap="Revenues more heavily impacted for dine-in only establishments", fig.width=6, fig.height=4, echo = FALSE, message = FALSE, warning = FALSE, out.width = '70%', fig.align = "center"}
survey_2 %>%
  filter(service_type != "NA") %>%
  ggplot(aes(x = service_type, y = revenue / 1000, fill = group)) +
  geom_bar(position = "dodge", stat = "summary", fun.y = mean) +
  labs(fill = NULL,
       x = "Service type provided",
       y = "Mean revenue (in thousands of Canadian dollars") +
  scale_x_discrete(labels = c( "Dine-in Only", "Take-out only", "Both")) +
  theme_minimal()
```

@@

```{r minorityimpact, fig.cap="Minority-owned businesses were more heavily impacted", fig.width=5, fig.height=4, echo = FALSE, message = FALSE, warning = FALSE, out.width = '70%', fig.align = "center"}
bind_rows(
  survey_2 %>%
    filter(indigenous == "yes" | visible == "yes") %>%
     mutate(minority = "Visible minority / Indigenous")
  ,
  survey_2 %>%
   filter(indigenous == "no" & visible == "no") %>%
    mutate(minority = "No")
) %>% 
  mutate(minority = fct_relevel(minority, "Visible minority / Indigenous", "No")) %>%
  ggplot(aes(x = minority, y = revenue / 1000, fill = group)) +
  geom_bar(position = "dodge", stat = "summary", fun.y = mean) +
  labs(fill = NULL,
       x = "Racial and ethnic minorities",
       y = "Mean revenue (in thousands of Canadian dollars") +
  theme_minimal()
```

@@

```{r nonresponse, fig.cap="More than half of surveyed restaurants did not respond", fig.width=8, fig.height=4, echo = FALSE, message = FALSE, warning = FALSE}
num_treat_sample <- as.numeric(count(table_for_surveys %>% filter(group == "treatment")))

@@

tibble(Group = c("Treatment", "Control", "Treatment", "Control", "Treatment", "Control", "Treatment", "Control", "Treatment", "Control", "Treatment", "Control"), 
        Response = c("Complete", "Complete", "Partial", "Partial", "No response", "No response", "Complete", "Complete", "Partial", "Partial", "No response", "No response"), 
        Survey = c("Survey 1", "Survey 1","Survey 1","Survey 1","Survey 1","Survey 1", "Survey 2", "Survey 2", "Survey 2", "Survey 2", "Survey 2", "Survey 2"), 
        Count = c(num_treat_complete_survey1, num_control_complete_survey1, num_treat_partial_survey1, num_control_partial_survey1, num_treat_nonre_survey1, num_control_nonresurvey1,
          num_treat_complete_survey2, num_control_complete_survey2, num_treat_partial_survey2, num_control_partial_survey2, num_treat_nonre_survey2, num_control_nonresurvey2)) %>%
  ggplot(aes(x = Response, y = Count, fill = Group)) +
  geom_bar(stat = "identity", position = "dodge") +
  facet_wrap(~Survey) +
  theme_minimal()

@@

```{r echo=FALSE, message=FALSE, warning=FALSE}
restaurants = 2006
survey_total = 2
indiv_postage = 0.85 # https://www.canadapost.ca/cpc/en/business/postal-services/mailing/letter-discounts.page?
minimum_wage = 14.25 # https://www.ontario.ca/document/your-guide-employment-standards-act-0/minimum-wage
management_service = 195 # https://www.alchemer.com/plans-pricing/small-teams/
average_call_mins = 7
response_rate = .3

>>>>

The COVID-19 pandemic has presented challenges that continue to test our resilience, creativity, and ability to recover. From online learning to curbside shopping, the changes are tangible on a local level. To better understand the impact of intermittent lockdowns on restaurant businesses specifically, and to provide the Ontario Ministry of Economic Development, Job Creation and Trade with evidence-based advice, Petit Poll conducted a comprehensive study of over 1,200 restaurants in 12 regions of Ontario. This report describes the experiment design and rationale, measurement strategies, data characteristics, main findings, recommendations, limitations, and broader implications. Importantly, the intervention revealed three key effects of closures: (1) closures had a negative impact on revenues and employment counts, (2) closures had a stronger negative impact on dine-in only restaurants, and (3) closures had a stronger negative impact on Indigenous or visible minority-owned businesses. These findings provide more detail to an already stark picture: while the health of Ontarians has to be prioritized, and the transmission of COVID-19 has to be aggressively contained, it is impossible to ignore the economic consequences of prolonged business closures. In particular, support for Indigenous and visible minority-owned businesses is imperative, as these populations continue to bear the brunt of systemic inequalities. Preparing and supporting dine-in establishments to transition to takeout only, and providing furloughed workers with vital financial support, must be equally prioritized.

@@

```{r treatmentcontrolgroups, echo = FALSE, message = FALSE, warning = FALSE}
treatment_control_groups %>%
  knitr::kable(caption = "Cluster sample randomly selecting Local Health Authorities from strata based on population size",
               booktabs = TRUE) %>%
  kableExtra::kable_styling() %>%
  collapse_rows()
```

@@

This survey cost $6711.18. A detailed breakdown of costs can be found on [Appendix A](#appendixA).

@@

survey_2 <- read_csv(here("outputs/data/survey_2.csv")) %>%
    mutate(group = fct_relevel(group, "treatment", "control"),
           service_type = fct_relevel(service_type, "dinein", "takeout", "both"),
           disability = fct_relevel(disability, "yes", "no", "nonanswer"),
           woman = fct_relevel(woman, "yes", "no", "nonanswer"),
           indigenous = fct_relevel(indigenous, "yes", "no", "nonanswer"),
           visible = fct_relevel(visible, "yes", "no", "nonanswer"))

count(full_join(survey_1, survey_2, by = "ID"))
```

@@

The initial survey provided an overview of the characteristics of the treatment and control groups. As indicated in Table \@ref(tab:survey1summary), the groups are equivalent, showing no notable differences across any of the variables studied. It was necessary to collect data before the intervention to ensure that the treatment and control groups were in fact comparable.

Survey 1 data was used to effectively establish a baseline for comparison. In addition to the use of random selection of participants and random assignment to either treatment or control, establishing a baseline allows for an accurate estimation of the counterfactual. The counterfactual – or the representation of what would have happened had the intervention not taken place – is essential to measuring, and reporting on, the effect of the mandated restaurant closures.

Figure \@ref(fig:baselinerevenue) Figure \@ref(fig:baselineemployees)

@@

```{r survey1summary, echo = FALSE, message = FALSE, warning = FALSE}
survey_1 %>% 
  summary_factorlist("group", c("service_type", "disability", "woman", "indigenous", "visible", "revenue", "ft", "pt"),
                     p = FALSE, 
                     add_dependent_label = TRUE,
                     dependent_label_prefix = "",
                     add_col_totals = TRUE,
                     include_row_missing_col = FALSE,
                     col_totals_rowname = "",
                     total_col = FALSE,
                     col_totals_prefix = "N (%) = ") %>%
  mutate(group = c("", "Service type", "", "", "Owner has disability", "", "", "Owner identifies as woman", "", "", "Owner is indigenous", "", "", "Owner is a visible minority (non-Indigenous)", "", "", "Revenue", "Number of full-time employees", "Number of part-time employees")) %>%
  knitr::kable(caption = "Summary statistics for treatment and control baselines",
               booktabs = TRUE, linesep = "",
               col.names = c("", "", "Treatment", "Control")) %>%
  kableExtra::kable_styling(latex_options = "striped", stripe_index =c(1,5:7,11:13,17:19))
```

```{r baselinerevenue, fig.cap="Revenue distribution for treatment and control baselines, from Survey 1", fig.width=10, fig.height=4, echo = FALSE, message = FALSE, warning = FALSE}
ggplot(survey_1, aes(x = revenue / 1000, fill = group)) +                       
  geom_histogram(position = "dodge", binwidth = 5) +
  theme_minimal() +
  scale_x_continuous(limits = c(0, 250), breaks = c(0, 50, 100, 150, 200, 250, 300)) +
  labs(fill = NULL,
       x = "Revenue in May 2021 (in thousands of Canadian dollars)",
       y = "Number of restaurants",
       title = "Revenue distributions were similar in the treatment and control samples")
```

@@

grid.arrange(p1, p2, ncol = 2, top = "Employment distributions were similar in the treatment and control samples")
```

@@

The second survey results showed marked differences between treatment and control groups in most areas. A summary of these results is found in Table \@ref(tab:survey2summary). Naturally, a salient difference is found in service type, with dine-in restaurants decreasing due to mandated shutdowns – the intervention itself – with 7% of restaurants in the control group providing dine-in service, and only 4% in the treatment group. Similarly, the mean revenue decreases noticeably for the treatment group (\$45,959.60) compared to the control group ($70675.60). The mean number of employees, both full-time and part-time, shows a decrease as well, from 8 and 5 respectively in the control group, to 5 and 3 for the treatment.

```{r survey2summary, echo = FALSE, message = FALSE, warning = FALSE}
survey_2 %>% 
  summary_factorlist("group", c("service_type", "disability", "woman", "indigenous", "visible", "shutdown", "revenue", "ft", "pt"),
                     p = FALSE, 
                     add_dependent_label = TRUE, 
                     dependent_label_prefix = "",
                     add_col_totals = TRUE,
                     include_row_missing_col = FALSE,
                     col_totals_rowname = "",
                     total_col = FALSE,
                     col_totals_prefix = "N (%) = ") %>%
  mutate(group = c("", "Service type", "", "", "Owner has disability", "", "", "Owner identifies as woman", "", "", "Owner is indigenous", "", "", "Owner is a visible minority (non-Indigenous)", "", "", "Closure", "", "", "Revenue", "Number of full-time employees", "Number of part-time employees")) %>%
  knitr::kable(caption = "Summary statistics for treatment and control groups post-treatment",
               booktabs = TRUE, linesep = "",
               col.names = c("", "", "Treatment", "Control")) %>%
   kableExtra::kable_styling(latex_options = "striped", stripe_index =c(1,5:7,11:13,17:19))
```

@@

Understanding the impact of COVID-19 closures of small businesses can help the Government of Ontario prepare to rebuild once the immediate health treat is contained. In particular, the contributions of restaurant businesses to the local economy have to be studied in terms of employment and revenue generation. According to The Associated Press, there was a 20% decline in employment in the restaurant, hotel, and entertainment sector between November 2019 and November 2020[@ap]. The National Restaurant Association reports a total loss industry-wide of $120 billion between March and May 2020 alone [@rd]. Although these figures are based on United States data, the findings from our experiment show a similarly concerning reality in Ontario. Swift action to protect and uplift the local economy will be crucial in the upcoming months.

@@

```{r postrevenue, fig.cap="Revenue distribution for treatment and control groups, from Survey 2", fig.width=10, fig.height=4, echo = FALSE, message = FALSE, warning = FALSE}
ggplot(survey_2, aes(x = revenue / 1000, fill = group)) +                       
  geom_histogram(position = "dodge", binwidth = 5) +
  theme_minimal() +
  scale_x_continuous(breaks = c(0, 50, 100, 150, 200, 250, 300)) +
  labs(fill = NULL,
       x = "Revenue in July 2021 (in thousands of Canadian dollars)",
       y = "Number of restaurants",
       title = "The revenue distribution was lower for the treatment sample")
```

@@

grid.arrange(p1, p2, ncol = 2, top = "Employment distributions were lower for the treatment sample")
```

@@

```{r servicetypeimpact, fig.cap = "Survey 2 revenue distributions for service types with means marked", fig.width=7, fig.height=5, echo = FALSE, message = FALSE, warning = FALSE, out.width = '70%', fig.align = "center"}
# from https://stackoverflow.com/questions/47651868/split-violin-plot-with-ggplot2-with-quantiles

GeomSplitViolin <- ggproto("GeomSplitViolin", GeomViolin, draw_group = function(self, data, ..., draw_quantiles = NULL){
  data <- transform(data, xminv = x - violinwidth * (x - xmin), xmaxv = x + violinwidth * (xmax - x))
  grp <- data[1,'group']
  newdata <- plyr::arrange(transform(data, x = if(grp%%2==1) xminv else xmaxv), if(grp%%2==1) y else -y)
  newdata <- rbind(newdata[1, ], newdata, newdata[nrow(newdata), ], newdata[1, ])
  newdata[c(1,nrow(newdata)-1,nrow(newdata)), 'x'] <- round(newdata[1, 'x']) 
  if (length(draw_quantiles) > 0 & !scales::zero_range(range(data$y))) {
    stopifnot(all(draw_quantiles >= 0), all(draw_quantiles <= 
                                              1))
    quantiles <- create_quantile_segment_frame(data, draw_quantiles)
    aesthetics <- data[rep(1, nrow(quantiles)), setdiff(names(data), c("x", "y")), drop = FALSE]
    aesthetics$alpha <- rep(1, nrow(quantiles))
    both <- cbind(quantiles, aesthetics)
    quantile_grob <- GeomPath$draw_panel(both, ...)
    ggplot2:::ggname("geom_split_violin", grobTree(GeomPolygon$draw_panel(newdata, ...), quantile_grob))
  }
  else {
    ggplot2:::ggname("geom_split_violin", GeomPolygon$draw_panel(newdata, ...))
  }
})

geom_split_violin <- function (mapping = NULL, data = NULL, stat = "ydensity", position = "identity", ..., draw_quantiles = NULL, trim = TRUE, scale = "area", na.rm = FALSE, show.legend = NA, inherit.aes = TRUE) {
  layer(data = data, mapping = mapping, stat = stat, geom = GeomSplitViolin, position = position, show.legend = show.legend, inherit.aes = inherit.aes, params = list(trim = trim, scale = scale, draw_quantiles = draw_quantiles, na.rm = na.rm, ...))
}

means <- survey_2 %>%
  filter(service_type != "NA" & revenue != "NA") %>%
  group_by(group, service_type) %>%
  summarise(mean = mean(revenue) / 1000)

ggplot() +
  geom_split_violin(data = (survey_2 %>% filter(service_type != "NA")), aes(x = service_type, y = revenue / 1000, fill = group), color = NA) +
  geom_errorbar(data = means, aes(x = service_type, y = mean, ymax = mean, ymin = mean, fill = group), position = "dodge") +
  labs(fill = NULL,
       x = "Service type provided",
       title = "Revenues were more heavily impacted for dine-in only establishments",
       y = "Revenue (in thousands of Canadian dollars)") +
  scale_x_discrete(labels = c( "Dine-in Only", "Take-out only", "Both")) +
  theme_minimal()
```

@@

```{r minorityimpact, fig.cap="Survey 2 revenue distributions for minority status with means marked", fig.width=6, fig.height=5, echo = FALSE, message = FALSE, warning = FALSE, out.width = '70%', fig.align = "center"}
data <- bind_rows(
  survey_2 %>%
    filter(indigenous == "yes" | visible == "yes") %>%
     mutate(minority = "Visible minority / Indigenous")
  ,
  survey_2 %>%
   filter(indigenous == "no" & visible == "no") %>%
    mutate(minority = "No")
) %>% 
  mutate(minority = fct_relevel(minority, "Visible minority / Indigenous", "No"))

means <- data %>%
  filter(service_type != "NA" & revenue != "NA") %>%
  group_by(group, minority) %>%
  summarise(mean = mean(revenue) / 1000)

ggplot() +
  geom_split_violin(data = data, aes(x = minority, y = revenue / 1000, fill = group), color = NA) +
  geom_errorbar(data = means, aes(x = minority, y = mean, ymax = mean, ymin = mean, fill = group), position = "dodge") +
  labs(fill = NULL,
       x = "Racial and ethnic minorities",
       title = "Minority-owned businesses were more heavily impacted",
       y = "Revenue (in thousands of Canadian dollars)") +
  theme_minimal()
```

@@

```{r nonresponse, fig.cap="Nonresponse and partial response rates for Survey 1 and 2", fig.width=8, fig.height=4, echo = FALSE, message = FALSE, warning = FALSE}
num_treat_sample <- as.numeric(count(table_for_surveys %>% filter(group == "treatment")))

@@

tibble(Group = c("Treatment", "Control", "Treatment", "Control", "Treatment", "Control", "Treatment", "Control", "Treatment", "Control", "Treatment", "Control"), 
        Response = c("Complete", "Complete", "Partial", "Partial", "No response", "No response", "Complete", "Complete", "Partial", "Partial", "No response", "No response"), 
        Survey = c("Survey 1", "Survey 1","Survey 1","Survey 1","Survey 1","Survey 1", "Survey 2", "Survey 2", "Survey 2", "Survey 2", "Survey 2", "Survey 2"), 
        Count = c(num_treat_complete_survey1, num_control_complete_survey1, num_treat_partial_survey1, num_control_partial_survey1, num_treat_nonre_survey1, num_control_nonresurvey1,
          num_treat_complete_survey2, num_control_complete_survey2, num_treat_partial_survey2, num_control_partial_survey2, num_treat_nonre_survey2, num_control_nonresurvey2)) %>%
  ggplot(aes(x = Response, y = Count, fill = Group)) +
  geom_bar(stat = "identity", position = "dodge") +
  labs(title = "More than half of surveyed restaurants did not respond") +
  facet_wrap(~Survey) +
  theme_minimal()

@@

```{r echo=FALSE, message=FALSE, warning=FALSE}
restaurants = 2006
survey_total = 2
indiv_postage = 0.85 # https://www.canadapost.ca/cpc/en/business/postal-services/mailing/letter-discounts.page?
minimum_wage = 14.25 # https://www.ontario.ca/document/your-guide-employment-standards-act-0/minimum-wage
management_service = 1300 # https://www.alchemer.com/plans-pricing/small-teams/
average_call_mins = 7
response_rate = .3

### 2021-02-20 scripts/extra_graphs_tables_for_paper.Rmd
add lorena's text and update graphs

>>>>

```{r}
bind_rows(
  survey_2 %>%
    filter(indigenous == "yes" | visible == "yes") %>%
     mutate(minority = "Visible minority / Indigenous")
  ,
  survey_2 %>%
   filter(indigenous == "no" & visible == "no") %>%
    mutate(minority = "No")
) %>% 
  mutate(minority = fct_relevel(minority, "Visible minority / Indigenous", "No")) %>%
  ggplot(aes(x = minority, y = revenue / 1000, fill = group)) +
  geom_violin() +
  labs(fill = NULL,
       x = "Racial and ethnic minorities",
       y = "Mean revenue (in thousands of Canadian dollars") +
  theme_minimal()
```

```{r}
bind_rows(
  survey_2 %>%
    filter(indigenous == "yes" | visible == "yes") %>%
     mutate(minority = "Visible minority / Indigenous")
  ,
  survey_2 %>%
   filter(indigenous == "no" & visible == "no") %>%
    mutate(minority = "No")
) %>% 
  mutate(minority = fct_relevel(minority, "Visible minority / Indigenous", "No")) %>%
  ggplot(aes(x = minority, y = revenue / 1000, fill = group)) +
  geom_split_violin() +
  labs(fill = NULL,
       x = "Racial and ethnic minorities",
       y = "Mean revenue (in thousands of Canadian dollars") +
  theme_minimal()
```

```{r}
bind_rows(
  survey_2 %>%
    filter(indigenous == "yes" | visible == "yes") %>%
     mutate(minority = "Visible minority / Indigenous")
  ,
  survey_2 %>%
   filter(indigenous == "no" & visible == "no") %>%
    mutate(minority = "No")
) %>% 
  mutate(minority = fct_relevel(minority, "Visible minority / Indigenous", "No")) %>%
  ggplot(aes(x = minority, y = revenue / 1000, fill = group)) +
  geom_violin() +
  labs(fill = NULL,
       x = "Racial and ethnic minorities",
       y = "Mean revenue (in thousands of Canadian dollars") +
  theme_minimal()
```

```{r servicetypeimpactx, fig.cap="Revenues more heavily impacted for dine-in only establishments", fig.width=6, fig.height=4, echo = FALSE, message = FALSE, warning = FALSE, out.width = '70%', fig.align = "center"}
survey_2 %>%
  filter(service_type != "NA") %>%
  ggplot(aes(x = service_type, y = revenue / 1000, fill = group)) +
  geom_bar(position = "dodge", stat = "summary", fun.y = mean) +
  labs(fill = NULL,
       x = "Service type provided",
       y = "Mean revenue (in thousands of Canadian dollars") +
  scale_x_discrete(labels = c( "Dine-in Only", "Take-out only", "Both")) +
  theme_minimal()
```

```{r minorityimpactx, fig.cap="Minority-owned businesses were more heavily impacted", fig.width=4.5, fig.height=4, echo = FALSE, message = FALSE, warning = FALSE, out.width = '60%', fig.align = "center"}
bind_rows(
  survey_2 %>%
    filter(indigenous == "yes" | visible == "yes") %>%
     mutate(minority = "Visible minority / Indigenous")
  ,
  survey_2 %>%
   filter(indigenous == "no" & visible == "no") %>%
    mutate(minority = "No")
) %>% 
  mutate(minority = fct_relevel(minority, "Visible minority / Indigenous", "No")) %>%
  ggplot(aes(x = minority, y = revenue / 1000, fill = group)) +
  geom_bar(position = "dodge", stat = "summary", fun.y = mean) +
  labs(fill = NULL,
       x = "Racial and ethnic minorities",
       y = "Mean revenue (in thousands of Canadian dollars") +
  theme_minimal()
```
